The \dealii{} Library, Version 9.2

### 2020-06-03 9.2/paper.tex
leave a todo
Fix some typos

 \author[*1]{Daniel Arndt}
 \affil[1]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   \texttt{arndtd/turcksinbr@ornl.gov}}

@@

The way the batch optimizer may be employed within a user's code is shown
in the pseudo-code below.
As per usual, one would first define some independent variables, and
subsequently compute some symbolic expressions that are dependent on these
independent variables.
These expression could be, for example, scalar  expressions or tensors of
expressions.
Instead of evaluating these expressions directly, the user would now create an
optimizer to evaluate the dependent functions.
In this example, the selected arithmetic type numerical result will be of type
\texttt{double}, and the \texttt{LLVM} JIT optimizer will be invoked.
It will employ common subexpression elimination and aggressive optimizations
during compilation.
The user then informs the optimizer of all of the independent variables and the
dependent expressions, and invokes the optimization process.
This is an expensive call, as it determines an equivalent code path to evaluate
all of the dependent functions at once.
However, in many cases each evaluation has significantly less computational cost
than evaluating the symbolic expressions directly.
Evaluation is performed when the user constructs a substitution map, giving each
independent variable a numerical representation, and passes those to the
optimizer.
After this step, the numerical equivalent of the individual dependent expressions
may finally be retreived from the optimizer.

@@

\begin{floatingfigure}[r]{0.3\textwidth}
  \centering
  \vspace*{-1.4cm}
  \includegraphics[width=0.3\textwidth]{python_mesh.png}
  \vspace*{-5mm}
  \caption{\it The mesh generated by the Python code shown in the main
    text. Cells are colored by material id.}
  \vspace*{0.2cm}
  \label{fig:pymesh}
\end{floatingfigure}
All triangulations created from within Python are serial. However,
once the mesh is designed, the triangulation can be serialized along
with the auxiliary information about possible refinement, boundaries,
materials and manifolds. This object can be easily deserialized within
a C++ program for subsequent production runs. Furthermore, such a
serialized triangulation can also be used in the construction of
\texttt{parallel::shared}, \texttt{parallel::disrtibuted}, and
\texttt{parallel::fullydistributed} triangulations (see also Section~\ref{subsec:pft}).

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
{around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item Two functions that provide information about all processes,
        namely
        \begin{itemize}
          \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
          \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
        \end{itemize}
        have been deprecated. As discussed in
        Subection~\ref{subsec:performance}, \dealii{} by default no longer
        stores information for all processes on all processes, but only
        local or locally-relevant information. On the other
        hand, if necessary, global information can still be computed using,
        for example, calling
        \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.

@@

>>>>

 \author[*1]{Daniel Arndt}
 \affil[1]{Computational Engineering and Energy Sciences Group,
   Computational Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   \texttt{arndtd/turcksinbr@ornl.gov}}

@@

The way the batch optimizer may be employed within a user's code is shown
in the pseudo-code below.
As per usual, one would first define some independent variables, and
subsequently compute some symbolic expressions that are dependent on these
independent variables.
These expression could be, for example, scalar  expressions or tensors of
expressions.
Instead of evaluating these expressions directly, the user would now create an
optimizer to evaluate the dependent functions.
In this example, the selected arithmetic type numerical result will be of type
\texttt{double}, and the \texttt{LLVM} JIT optimizer will be invoked.
It will employ common subexpression elimination and aggressive optimizations
during compilation.
The user then informs the optimizer of all of the independent variables and the
dependent expressions, and invokes the optimization process.
This is an expensive call, as it determines an equivalent code path to evaluate
all of the dependent functions at once.
However, in many cases each evaluation has significantly less computational cost
than evaluating the symbolic expressions directly.
Evaluation is performed when the user constructs a substitution map, giving each
independent variable a numerical representation, and passes those to the
optimizer.
After this step, the numerical equivalent of the individual dependent expressions
may finally be retrieved from the optimizer.

@@

\begin{floatingfigure}[r]{0.3\textwidth}
  \centering
  \vspace*{-1.4cm}
  \includegraphics[width=0.3\textwidth]{python_mesh.png}
  \vspace*{-5mm}
  \caption{\it The mesh generated by the Python code shown in the main
    text. Cells are colored by material id.}
  \vspace*{0.2cm}
  \label{fig:pymesh}
\end{floatingfigure}
All triangulations created from within Python are serial. However,
once the mesh is designed, the triangulation can be serialized along
with the auxiliary information about possible refinement, boundaries,
materials and manifolds. This object can be easily deserialized within
a C++ program for subsequent production runs. Furthermore, such a
serialized triangulation can also be used in the construction of
\texttt{parallel::shared}, \texttt{parallel::distributed}, and
\texttt{parallel::fullydistributed} triangulations (see also Section~\ref{subsec:pft}).

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
{around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item Two functions that provide information about all processes,
        namely
        \begin{itemize}
          \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
          \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
        \end{itemize}
        have been deprecated. As discussed in
        Subsection~\ref{subsec:performance}, \dealii{} by default no longer
        stores information for all processes on all processes, but only
        local or locally-relevant information. On the other
        hand, if necessary, global information can still be computed using,
        for example, calling
        \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.

@@

\todo[inline]{Timo needs to fix his support}
